% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\usepackage[colorlinks,linkcolor=blue]{hyperref}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Jianpeng Hou}
\centerline{Data Mining; Software Development}
\vspace{2ex}
% {E-mail}{mobilephone}{homepage}
% be careful of _ in emaill address
% {E-mail}{mobilephone}
% keep the last empty braces!
\contactInfo{houjp1992@gmail.com}{(+86) 152-0144-2067}{ \url{https://github.com/houjp/}}

 
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Institute of Computer Technology, Chinese Academy of Sciences}}{Sep. 2014 -- Jul. 2017}
\textit{Master student} in Computer Software \& Theory, Rank: top 5\%
\datedsubsection{\textbf{University of Science \& Technology Beijing}}{Sep. 2010 -- Jul. 2014}
\textit{Bachelor student} in Computer Science \& Technology, Rank: 4/203

\section{\faUsers\ Project Experience}
\datedsubsection{\textbf{Big Data Analysis Platform}}{Oct. 2015 -- Mar. 2016}
%\role{Summer Intern}{Manager: xxx}
\begin{itemize}
  \item  Developed distributed algorithms(CART/GBDT/GBRT/RF) on Spark.
  \item Finished data mining components(Feature-Indexing/Feature-Merging/Feature-Normalization/Scoring).
%  \item Optimized xxx 5\%
\end{itemize}

\datedsubsection{\textbf{China Telecom Big Data Application Contest (1st/1112)}}{Dec. 2015 -- Mar. 2016}
%\role{C, Python, Django, Linux}{Individual Projects, collaborated with xxx}
The goal of this contest is to predict views of users with ten sites succeeding, according to four hundred million user-behavior historical records(25.38G).
%Brief introduction: xxx
\begin{itemize}
  \item Proposed and implemented a multi-target regression algorithm on Spark. Optimized F1-score 0.8\%.
  \item Designed and developed a probability ranking model for user classification. Optimized F1-score  0.6\%.
%  \item xxx
\end{itemize}

\datedsubsection{\textbf{SIGHAN-2015 Chinese Spelling Check Task}}{Mar. 2015 -- May. 2015}
%\role{\LaTeX, Maintainer}{Individual Projects}
The goal of this task is to detect and correct spelling errors on Chinese essays.
\begin{itemize}
  \item Handled this task with a unified framework which consisted of candidate generating, two stage candidates re-ranking and global decision making.
  \item Finished candidate generating model and two stage candidates re-ranking model. Optimized F1-score 18\%.
\end{itemize}

\section{\faSitemap\ Practice Experience}

\datedsubsection{\textbf{DiDi Research Institute}}{Jul. 2016 -- Aug. 2016}
%\role{\LaTeX, Maintainer}{Individual Projects}
%The goal of this task was to detect and correct spelling errors on Chinese essays.
\begin{itemize}
  \item Developed taxi dispatching system which used to balance the supply and demand between urban areas.
  \item Reconstructed the log system of dispatching based on Kafka and MySQL.
\end{itemize}

\datedsubsection{\textbf{Baidu Online Network Technology(Beijing) Co.,Ltd}}{Dec. 2013 -- May. 2014}
%\role{\LaTeX, Maintainer}{Individual Projects}
%The goal of this task was to detect and correct spelling errors on Chinese essays.
\begin{itemize}
  \item Completed the multi-threaded development of LiveWDBBroom, improved the efficiency by two times.
  \item Completed the development of the Problems-Tracing Platform which was put into service.
  \item Passed the examination of Code Master(C++), certified as Good Coder.
\end{itemize}


% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}


\section{\faTrophy\ Academic Competitions}
\datedline{\textit{\nth{1} Place}~~Awarded in China Telecom Big Data Application Contest}{Mar. 2016}
\datedline{\textit{\nth{1} Place}~~Awarded in SIGHAN-2015 Chinese Spelling Check Task}{Jun. 2015}
\datedline{\textit{\nth{1} Place}~~Awarded in China College Students Computer Games Competition}{Nov. 2013}
\datedline{\textit{\nth{1} Prize}~~Awarded in China College Students Computer Application Contest}{Nov. 2013}
\datedline{\textit{\nth{1} Prize}~~Awarded in ”LanQiao Cup” Software Development Contest(Beijing Division)}{Apr. 2012}
\datedline{\textit{Silver Medal~(\nth{17} / 200)}~~Awarded in ACM-ICPC Asia Beijing Regional Contest}{Nov. 2015}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Skilled in C++, Scala, Shell. Familiar with data structures and algorithms and had good programming style.
  \item Experienced in development of distributed machine learning algorithms.
  \item Strong theoretic knowledge on data mining and machine learning.
\end{itemize}


%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
