% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% !Mode:: "TeX:UTF-8"

\documentclass{resume}
\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\usepackage{linespacing_fix} % disable extra space before next section
\usepackage{cite}
\usepackage[colorlinks,linkcolor=blue]{hyperref}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number


\name{Jianpeng Hou}
\centerline{Machine Learning; Software Development}
\vspace{2ex}
% {E-mail}{mobilephone}{homepage}
% be careful of _ in emaill address
% {E-mail}{mobilephone}
% keep the last empty braces!
\contactInfo{houjp1992@gmail.com}{(+86) 152-0000-0000}{ \url{https://github.com/houjp/}}

 
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Institute of Computer Technology, Chinese Academy of Sciences}}{Sep. 2014 -- Jul. 2017}
\textit{Master student} in Computer Software \& Theory, Rank: top 5\%
\datedsubsection{\textbf{University of Science \& Technology Beijing}}{Sep. 2010 -- Jul. 2014}
\textit{Bachelor student} in Computer Science \& Technology, Rank: \nth{4}/124

\section{\faUsers\ Project Experience}
\datedsubsection{\textbf{Big Data Analysis Platform (\href{http://159.226.40.104:18080}{http://159.226.40.104:18080})}}{Oct. 2015 -- Mar. 2016}
%\role{Summer Intern}{Manager: xxx}
\begin{itemize}
  \item  Developed distributed algorithms(CART/GBDT/GBRT/RF) on Spark.
  \item Finished data mining components(Feature-Indexing/Feature-Merging/Feature-Normalization/Scoring).
%  \item Optimized xxx 5\%
\end{itemize}

\datedsubsection{\textbf{China Telecom Big Data Application Contest (\nth{1}/1112; Team Leader)}}{Dec. 2015 -- Mar. 2016}
%\role{C, Python, Django, Linux}{Individual Projects, collaborated with xxx}
The goal of this contest is to predict views of users with ten sites succeeding, according to four hundred million user-behavior historical records(25.38G).
%Brief introduction: xxx
\begin{itemize}
  \item Proposed and implemented a multi-target regression algorithm on Spark. Optimized F1-score 0.8\%.
  \item Designed and developed a probability ranking model for user classification. Optimized F1-score  0.6\%.
%  \item xxx
\end{itemize}

\datedsubsection{\textbf{SIGHAN-2015 Chinese Spelling Check Task (\nth{1} Place)}}{Mar. 2015 -- May. 2015}
%\role{\LaTeX, Maintainer}{Individual Projects}
The goal of this task is to detect and correct spelling errors on Chinese essays.
\begin{itemize}
  \item Handled this task with a unified framework which consisted of candidate generating, two stage candidates re-ranking and global decision making.
  \item Finished candidate generating model and two stage candidates re-ranking model. Optimized F1-score 18\%.
\end{itemize}

\section{\faSitemap\ Intern Experience}

\datedsubsection{\textbf{DiDi Research Institute}}{Jul. 2016 -- Sep. 2016}
%\role{\LaTeX, Maintainer}{Individual Projects}
%The goal of this task was to detect and correct spelling errors on Chinese essays.
\begin{itemize}
  \item Developed taxi dispatching system which used to balance the supply and demand between urban areas.
  \item Reconstructed the log system of dispatching based on Kafka and MySQL.
\end{itemize}

\datedsubsection{\textbf{Baidu Online Network Technology(Beijing) Co.,Ltd}}{Dec. 2013 -- May. 2014}
%\role{\LaTeX, Maintainer}{Individual Projects}
%The goal of this task was to detect and correct spelling errors on Chinese essays.
\begin{itemize}
  \item Completed the multi-threaded development of LiveWDBBroom, improved the efficiency by two times.
  \item Completed the development of the Problems-Tracing Platform which was put into service.
  \item Passed the examination of Code Master(C++), certified as Good Coder.
\end{itemize}


% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}


\section{\faTrophy\ Academic Competitions}
\datedline{\textit{\nth{1} Place}~~Awarded in China Telecom Big Data Application Contest}{Mar. 2016}
\datedline{\textit{\nth{1} Place}~~Awarded in SIGHAN-2015 Chinese Spelling Check Task}{Jun. 2015}
\datedline{\textit{\nth{1} Place}~~Awarded in China College Students Computer Games Competition}{Nov. 2013}
\datedline{\textit{\nth{1} Prize}~~Awarded in China College Students Computer Application Contest}{Nov. 2013}
\datedline{\textit{\nth{1} Prize}~~Awarded in "LanQiao Cup" Software Development Contest(Beijing Division)}{Apr. 2012}
\datedline{\textit{Silver Medal~(\nth{17} / 200)}~~Awarded in ACM-ICPC Asia Beijing Regional Contest}{Nov. 2015}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Skilled in C++, Scala, Shell. Familiar with data structures and algorithms and had good programming style.
  \item Experienced in development of distributed machine learning algorithms.
  \item Strong theoretic knowledge on data mining and machine learning.
\end{itemize}



\name{侯建鹏 }
\centerline{求职意向: 机器学习 | 软件研发}
% {E-mail}{mobilephone}{homepage}
% be careful of _ in emaill address
\vspace{1ex}
\contactInfo{houjp1992@gmail.com}{(+86) 152-0000-0000}{ \url{https://github.com/houjp/} }


% {E-mail}{mobilephone}
% keep the last empty braces!
%\contactInfo{xxx@yuanbin.me}{(+86) 131-221-87xxx}{}

\vspace{-1ex}
 
\section{\faGraduationCap\  教育背景}
\datedsubsection{\textbf{中国科学院计算技术研究所(保送)}~~ \ 硕士, 计算机软件与理论, 排名: 5\%}{2014 -- 2017}

\datedsubsection{\textbf{北京科技大学}~~ \ 学士, 计算机科学与技术, 排名: \nth{4}/124}{2010 -- 2014}
\vspace{1ex}

%\vspace{-1ex}

\section{\faUsers\ 项目经历}
\datedsubsection{\textbf{BDA大数据分析系统 (\href{http://159.226.40.104:18080}{http://159.226.40.104:18080})} }{2015.10 -- 2016.03}
%\role{实习}{经理: 高富帅}
%xxx后端开发
\begin{itemize}
  \item 作为 BDA Lib 核心开发者,在分布式计算框架 Spark 上实现了 CART/GBDT/GBRT/RF 算法的 分布式版本,同时完成了这些算法单机版本的开发。
  \item 实现了 BDA Studio 中需要的数据挖掘基本组件 (包括特征索引、特征合并、特征选择、特征值 归一化、模型输出结果评分等功能),并构建真实场景的应用实例。
\end{itemize}

\vspace{-1.5ex}

\datedsubsection{\textbf{中国电信大数据竞赛 (\nth{1}/1112; CNY 200,000; 队长)}}{2015.12 -- 2016.03}
%\role{Golang, Linux}{个人项目，和富帅糕合作开发}
\begin{onehalfspacing}
根据海量用户行为数据(大于四亿条,25.38G),预测用户接下来一周对十个视频网
站的访问量。
\begin{itemize}
  \item 基于 Spark 分布式计算框架,提出并实现了 MTGBM 多目标回归算法,使得 F1 值提升 0.8\%。
  \item 提出并实现了用于用户分类的概率排序模型,使得 F1 值提升 0.6\%。
\end{itemize}
\end{onehalfspacing}

\vspace{-1.5ex}

\datedsubsection{\textbf{SIGHAN-2015 Chinese Spelling Check Task}}{2015.03 -- 2015.05}
%\role{\LaTeX, Python}{个人项目}
\begin{onehalfspacing}
该评测任务是对繁体中文进行拼写检查,给出正确的拼写结果。
\begin{itemize}
  \item 实现候选生成排序模型：根据同音、近音、形近字,为句中每一个繁体字生成候选, 并打分排序。
  \item 实现两轮候选重排序模型：采用简单特征进行预排序,在第一次排序的基础上结合复杂特征进行第二次排序,以此提高排序效率。最终取得第一名，F值超出第二名18\%。
\end{itemize}
\end{onehalfspacing}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\vspace{-1ex}

\section{\faSitemap\ 实习经历}
\datedsubsection{\textbf{滴滴研究院~智能平台部~/~算法工程师}}{2016.07 -- 2016.09}
\vspace{-0.5ex}
%\role{\LaTeX, Python}{个人项目}
\begin{onehalfspacing}
%优雅的 \LaTeX\ 简历模板, https://github.com/billryan/resume
\begin{itemize}
  \item 完成专车调度系统开发、测试并上线，实现对城市各区域专车供需不平衡状态的动态调整。
  \item 基于Kafka及MySQL完成专车调度日志系统重构，解耦子模块间相互依赖，提高系统可用性。
\end{itemize}
\end{onehalfspacing}

\vspace{-1.5ex}

\datedsubsection{\textbf{百度~网页搜索部~/~研发工程师}}{2013.12 -- 2014.05}
\vspace{-0.5ex}
%\role{\LaTeX, Python}{个人项目}
\begin{onehalfspacing}
\begin{itemize}
  \item  完成 livewdbbroom 工具多线程开发,通过测试并上线,效率提升 2 倍以上。
  \item 完成离线时效性日志体系建设及离线时效性问题追查平台建设,并上线。
  \item 通过 Code Master(C++) 考试,获得 Good Coder 认证。
\end{itemize}
\end{onehalfspacing}

\vspace{-1ex}

\section{\faTrophy\ 学术竞赛}
\datedline{\textit{冠军 (\nth{1}/1112; CNY 200,000; 队长)}~中国电信大数据算法应用大赛}{2016.03}
\datedline{\textit{冠军}~SIGHAN-2015 Chinese Spelling Check Task}{2015.06}
\datedline{\textit{冠军}~全国大学生计算机博弈大赛}{2013.08}
\datedline{\textit{银牌 (\nth{17}/200)}~ACM-ICPC 国际大学生程序设计竞赛亚洲区域赛北京赛区}{2015.11}
\datedline{\textit{四强 (\nth{4}/2293)}~阿里巴巴大数据竞赛“新浪微博互动预测大赛”}{2015.12}
\datedline{\textit{一等奖}~华北五省及港澳台大学生计算机应用大赛}{2013.11}
\datedline{\textit{一等奖}~全国软件专业人才设计与创业大赛北京赛区}{2012.04}

\vspace{-1ex}

\section{\faCogs\ 个人能力}
% increase linespacing [parsep=0.5ex]
\begin{itemize}[parsep=0.5ex]
  \item 熟悉 Scala、C++、Shell,熟悉基本数据结构和算法,有良好的编程风格。
  \item 有丰富的基于 Spark 分布式计算框架的机器学习算法开发经验。
  \item 熟悉数据挖掘、机器学习领域基本算法。
\end{itemize}

%\section{\faInfo\ 其他}
%% increase linespacing [parsep=0.5ex]
%\begin{itemize}[parsep=0.5ex]
%  \item 技术博客: http://blog.yours.me
%  \item GitHub: https://github.com/username
%  \item 语言: 英语 - 熟练(TOEFL xxx)
%\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
